### 2019-08-18 reports/thesis/chapters/1_literatureReview.tex
Update bib

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_3dprint.png}
  \caption{Examples of additive manufactured parts: a) lattice structure, b) toy, c) chain, d) model of a facial implant, e) spanner, f) ratchet mechanism, g) toy, h) series of rotatable gears, i) lattice structure. Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
  \label{fig:literature_3dprint}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.59\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_stl.png}
      \caption{Stereolithography}
    \end{subfigure}
    \begin{subfigure}[b]{0.39\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_fdm.png}
      \caption{Fused deposition modelling}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_3dp.png}
      \caption{3D printing}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_laser.png}
      \caption{Selective laser sintering}
    \end{subfigure}
  }
  \caption{Diagrams of various AM technologies. Reprinted from \cite{wang20173d} with permission from Elsevier.}
  \label{fig:literature_technologies}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD model (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
  \label{fig:literature_stl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_balling.png}
  \caption{A scanning electron microscope image of balling on a selective laser melting manufactured object. Reprinted from \cite{li2012balling} with permission from Springer Nature.}
  \label{fig:literature_balling}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.99\textwidth]{../figures/literatureReview/literature_medicalct.png}
  \caption{In medical XCT, a fan shaped x-ray beam is emitted and attenuate through the patient and detected by a detector. The x-ray source and detector rotate around and translate along the patient. By collecting readings at different angles, the image of the patient can be reconstructed. Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
  \label{fig:literature_medicalct}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{../figures/literatureReview/literature_tube.png}
  \caption{An x-ray tube. Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
  \label{fig:literature_tube}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/literatureReview/literature_spectrum.png}
  \caption{An example of the distribution of energies a photon can have emitted from an x-ray tube. Bremsstrahlung and characteristic radiation contribute to the continuous and discrete components of the distribution. Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
  \label{fig:literature_spectrum}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test1.png}
      \caption{Hollow cylinder}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test2.png}
      \caption{Step-cylinder}
    \end{subfigure}
  }
  \begin{subfigure}[b]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test3.png}
    \caption{Ball-bar}
  \end{subfigure}
  \caption{Various reference standards: a) aluminium hollow cylinder, outer diameters \SI{30}{\milli\metre} and \SI{20}{\milli\metre}, b) aluminium step-cylinder with diameter \SI{300}{\milli\metre}, c) ceramic balls of diameter \SI{30}{\milli\metre} on a carbon fibre rod, the balls are separated by \SI{100}{\milli\metre}. Reprinted from \citep{bartscher2007enhancement} with permission from Elsevier.}
  \label{fig:literature_referenceStandards}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
  \caption{The magnification can be adjusted by adjusting the distances between the x-ray source, the object and the x-ray detector. Because of a finite x-ray spot size, blurry effects are produced using a magnification too large. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
  \label{fig:literature_magnification}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}

@@

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}. Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate, called a filter, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper. Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{sun2016applications}.

\begin{figure}
  \centering
    \begin{subfigure}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_noFilter.png}
      \caption{No filter}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_filter.png}
      \caption{Al/Cu filter}
    \end{subfigure}
  \caption{A reconstruction of a hollow cylinder, outer diameter \SI{6.0}{\milli\metre} and inner diameter \SI{0.6}{\milli\metre}. In a), no filter was used. In b) a filter was placed in front of the x-ray tube. Reprinted from \citep{kruth2011computed} with permission from Elsevier}
  \label{fig:literature_hardening}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_3dprint.png}
  \caption{Examples of additive manufactured parts: a) lattice structure, b) toy, c) chain, d) model of a facial implant, e) spanner, f) ratchet mechanism, g) toy, h) series of rotatable gears, i) lattice structure. Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
Clearance Center, Inc.}
  \label{fig:literature_3dprint}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.59\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_stl.png}
      \caption{Stereolithography}
    \end{subfigure}
    \begin{subfigure}[b]{0.39\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_fdm.png}
      \caption{Fused deposition modelling}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_3dp.png}
      \caption{3D printing}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_laser.png}
      \caption{Selective laser sintering}
    \end{subfigure}
  }
  \caption{Diagrams of various AM technologies. Reprinted from \cite{wang20173d}\textsuperscript{\textcopyright}, with permission from Elsevier.}
  \label{fig:literature_technologies}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD model (left) converted to a STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
Clearance Center, Inc.}
  \label{fig:literature_stl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_balling.png}
  \caption{A scanning electron microscope image of balling on a selective laser melting manufactured object. Reprinted by permission from Springer Nature: \cite{li2012balling}\textsuperscript{\textcopyright}.}
  \label{fig:literature_balling}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.99\textwidth]{../figures/literatureReview/literature_medicalct.png}
  \caption{In medical XCT, a fan shaped x-ray beam is emitted and attenuate through the patient and detected by a detector. The x-ray source and detector rotate around and translate along the patient. By collecting readings at different angles, the image of the patient can be reconstructed. Reprinted from \cite{michael2001x}. \textcopyright\ IOP Publishing. Reproduced with permission. All rights reserved.}
  \label{fig:literature_medicalct}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{../figures/literatureReview/literature_tube.png}
  \caption{An x-ray tube. Reprinted from \cite{michael2001x}. \textcopyright\ IOP Publishing. Reproduced with permission. All rights reserved.}
  \label{fig:literature_tube}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/literatureReview/literature_spectrum.png}
  \caption{An example of the distribution of energies a photon can have emitted from an x-ray tube. Bremsstrahlung and characteristic radiation contribute to the continuous and discrete components of the distribution. Reprinted from \cite{michael2001x}. \textcopyright\ IOP Publishing. Reproduced with permission. All rights reserved.}
  \label{fig:literature_spectrum}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test1.png}
      \caption{Hollow cylinder}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test2.png}
      \caption{Step-cylinder}
    \end{subfigure}
  }
  \begin{subfigure}[b]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test3.png}
    \caption{Ball-bar}
  \end{subfigure}
  \caption{Various reference standards: a) aluminium hollow cylinder, outer diameters \SI{30}{\milli\metre} and \SI{20}{\milli\metre}, b) aluminium step-cylinder with diameter \SI{300}{\milli\metre}, c) ceramic balls of diameter \SI{30}{\milli\metre} on a carbon fibre rod, the balls are separated by \SI{100}{\milli\metre}. Reprinted from \cite{bartscher2007enhancement}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_referenceStandards}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
  \caption{The magnification can be adjusted by adjusting the distances between the x-ray source, the object and the x-ray detector. Because of a finite x-ray spot size, blurry effects are produced using a magnification too large. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_magnification}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}

@@

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}. Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate, called a filter, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper. Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{elbakri2001statistical, sun2016applications}.

\begin{figure}
  \centering
    \begin{subfigure}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_noFilter.png}
      \caption{No filter}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_filter.png}
      \caption{Al/Cu filter}
    \end{subfigure}
  \caption{A reconstruction of a hollow cylinder, outer diameter \SI{6.0}{\milli\metre} and inner diameter \SI{0.6}{\milli\metre}. In a), no filter was used. In b) a filter was placed in front of the x-ray tube. Reprinted from \citep{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier}
  \label{fig:literature_hardening}
\end{figure}

### 2019-08-18 reports/thesis/chapters/4_variancePrediction.tex

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction. The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsNoFilter}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction. The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsNoFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \caption{Log frequency density histogram of the residuals given the mean grey value. The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections. The dashed red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the predicted residual.}
  \label{fig:meanVar_residualGreyvalue}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction. The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsNoFilter}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction. The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsNoFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \caption{Log frequency density histogram of the residuals given the mean grey value. The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections. The dashed red line shows the 95\% confidence interval of the predicted residual.}
  \label{fig:meanVar_residualGreyvalue}
\end{figure}
